Red-Giant Hot Jupiters: Brilliant Radio Beacons?

### 2015-05-26 ms.tex
Description of Section 4 is edited so as to be consistent with Figure 3

For each red giant, the mass-loss rate is estimated by Reimers' equation \citep{reimers1975}:
%%%
\begin{equation}
\dot M_{\star } [M_{\odot }{\rm /yr}] \sim 4 \times 10^{-13} \left( \frac{R_{\star }}{R_{\odot }} \right)\left( \frac{L_{\star }}{L_{\odot }} \right) \left( \frac{M_{\star }}{M_{\odot }} \right)^{-1}
\end{equation}
%%%
where $R_{\star }$, $L_{\star } (=4\pi R_{\star }^2 T_{\star }^4)$, and $M_{\star}$ are radius, luminosity, and mass of the star. 
The velocity of stellar wind is assumed to scale with the escape velocity, hence
%%%
\begin{equation}
v \propto \sqrt{\frac{2GM_{\star }}{R_{\star }}}
\end{equation}
%%%
Using these values for equations (\ref{eq:stand-off}) and (\ref{eq:stand-off-radius}) as well as the distance to the target, we can estimate the frequency and intensity by specifying the magnetic field and orbital distance of a hypothetical planetary companion. 
Here, we consider two cases: (a) a Jupiter-twin at 5~AU whose cyclotron frequency is $\sim 30$~MHz, and (b) a larger Jovian planet with $M_p\sim 5M_p$ of 4.5 Gyrs old at 5~AU whose cyclotron frequency is $\sim 300$~MHz (equation (\ref{eq:scalingfc})).

Figure \ref{fig:observability} displays the estimated radio intensity and the maximum frequency (i.e., cyclotron frequency) of red giants within 100~pc.  
The difference of the symbols indicates whether the radio emission can escape from the system (circle) or not (cross).

>>>>

For each red giant, the mass-loss rate is estimated by Reimers' equation \citep{reimers1975}:
%%%
\begin{equation}
\dot M_{\star } [M_{\odot }{\rm /yr}] \sim 4 \times 10^{-13} \left( \frac{R_{\star }}{R_{\odot }} \right)\left( \frac{L_{\star }}{L_{\odot }} \right) \left( \frac{M_{\star }}{M_{\odot }} \right)^{-1}
\end{equation}
%%%
where $R_{\star }$, $L_{\star } (=4\pi R_{\star }^2 T_{\star }^4)$, and $M_{\star}$ are radius, luminosity, and mass of the star. 
The velocity of stellar wind is assumed to scale with the escape velocity, hence
%%%
\begin{equation}
v \propto \sqrt{\frac{2GM_{\star }}{R_{\star }}}
\end{equation}
%%%
Using these values for equations (\ref{eq:stand-off}) and (\ref{eq:stand-off-radius}) as well as the distance to the target, we can estimate the frequency and intensity of radio emission by specifying planetary mass and orbital distance of a hypothetical planetary companion. 
Here, we consider [A] a Jupiter-twin whose cyclotron frequency is $\sim 30$~MHz, and [B] a larger Jovian planet with $M_p\sim 5M_p$ of 4.5 Gyrs old whose cyclotron frequency is $\sim 300$~MHz (equation (\ref{eq:scalingfc})).

Figure \ref{fig:observability} displays the estimated radio intensity and the maximum frequency (i.e., cyclotron frequency) of Jupiters [A] and [B] around red giants within 100~pc. 
Jupiters [A] and [B] are placed at 1 AU and at 5 AU for reference. 
The difference of the symbols indicates whether the radio emission can escape from the system (circle) or not (cross).

\memoYF{Up to where would the planet be engulfed by evolved stars? References?}
